Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-29 sattose/paper.tex
Fixed a table
Changed the place

\author{
Simon Baars \\ University of Amsterdam\\
                Puiflijk, Netherlands \\ simon.mailadres@gmail.com
\and
Ana Oprescu \\ University of Amsterdam\\
                Amsterdam, Netherlands \\ A.M.Oprescu@uva.nl
}

@@

\begin{document}
\maketitle
% In this paper I talk about clone instances and clone classes. Should I explain those concepts first?

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents} \label{table:refactorability}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
Cannot directly be extracted    & 10,990           & 41.91               \\ \hline
Can be extracted                & 5,791            & 22.08               \\ \hline
Not possible because of content & 9,444            & 36.01               \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

\author{
Simon Baars \\ University of Amsterdam\\
                Amsterdam, Netherlands \\ simon.mailadres@gmail.com
\and
Ana Oprescu \\ University of Amsterdam\\
                Amsterdam, Netherlands \\ A.M.Oprescu@uva.nl
}

@@

\begin{document}
\maketitle

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance contents} \label{table:refactorability}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Refactorability}        & \textbf{Amount} & \textbf{Percentage} \\ \hline
\begin{tabular}[c]{@{}l@{}}Cannot directly\\be extracted\end{tabular}    & 10,990           & 41.91               \\ \hline
\begin{tabular}[c]{@{}l@{}}Is not a\\partial method\end{tabular} & 9,444            & 36.01               \\ \hline
\begin{tabular}[c]{@{}l@{}}Can be\\extracted\end{tabular}                & 5,791            & 22.08               \\ \hline

\end{tabular}
\end{center}
\end{table}
